\Large Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-01-24 paper/main.tex
quotation fix (thanks PCF!)

When we held the within-list variability in participants' visual experiences
fixed across lists (in the feature rich and reduced conditions), they
remembered more words from early lists than from late lists. For feature rich
lists, they also showed stronger clustering for early versus late lists.
However, when we \textit{varied} participants' visual experiences across lists
(in the ``reduced (early)'' and ``reduced (late)'' conditions), these early
versus late accuracy and clustering differences disappeared. Abruptly changing
how irrelevant visual features varied across words seemed to act as a sort of
``event boundary'' that partially reset how participants processed and
remembered post-boundary lists. Within-list clustering also increased in these
manipulations, suggesting that the "within-event" words were being more tightly
associated with each other.

>>>>

When we held the within-list variability in participants' visual experiences
fixed across lists (in the feature rich and reduced conditions), they
remembered more words from early lists than from late lists. For feature rich
lists, they also showed stronger clustering for early versus late lists.
However, when we \textit{varied} participants' visual experiences across lists
(in the ``reduced (early)'' and ``reduced (late)'' conditions), these early
versus late accuracy and clustering differences disappeared. Abruptly changing
how irrelevant visual features varied across words seemed to act as a sort of
``event boundary'' that partially reset how participants processed and
remembered post-boundary lists. Within-list clustering also increased in these
manipulations, suggesting that the ``within-event'' words were being more tightly
associated with each other.
